---
title: "mcdocs"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

R package of Methods Consultants branded RMarkdown templates

## Installation

To install the `mcdocs` package containing all of the Methods templates, run:

```{r eval = FALSE}
devtools::install_github("MethodsConsultants/mcdocs")
```

- To start a new document or presentation using a Methods template, create an RMarkdown document, navigate to the `From Template` screen on the sidebar and select which template you would like to use.

- Currently, there is only one template in the package: `Methods Consultants Presentation Slides`
    - This template two additional files that go along with it:
        1. `methods_slides.css` has the styling elements for the slides (i.e. background color, size of logo)
        2. `Methods-logo-rectangle.png` is the logo used on the slides
    - When you create the RMarkdown file from the template, the window prompts you to create a new directory to put these files in, so make sure you know where you want them to go on your machine.
